---
title: "Lecture Notes"
date: "`r Sys.Date()`"
output:   
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: show
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=FALSE, include=TRUE, results="hold", comment=NA)
```

## August 28, 2025

Question: What is the difference between a folder, a directory, and a Git repository?

1. Folder and directory are interchangeable
2. Git repo is a special type of folder
3. Hot key to Commit/stage -> CTRL + ALT + m
4. Hot key to actually commit is CTRL + m

## September 2, 2025

1. usethis::use_github() #Creates a git repository
2. usethis::use_github(private=True) # creates a private git repository
3. usethis::create_from_github("https://github.com/huensch/practice-repo.git")
4. usethis::create_from_github("https://github.com/Data-Sci-2025/Class-Exercise-Repo", fork=TRUE)

## Sept 4, 2025

1. todo checklist
  1. When creating a pull request, check:
    1. whether GitHub can merge your changes
    2. Files changed: Are they what you expect?
  2. 

### Markdown

1. Once you create a quatro document, it's a good idea to add a date
2. add this at the bottom of the
3. to get rid of the output below use the settings (Chunk output in console)

# Session info
```{r}
sessionInfo()
```

